%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
% Document margins
\usepackage{color,hyperref}
\usepackage{fontawesome}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Pavel Panko} % Your name
\address{Lubbock, TX} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary
%addess (optional)

\address{pavel.panko@ttu.edu
  \\ \faGithub \space \href{http://www.github.com/ppanko}{ppanko}
  \\ \faLinkedin \space \href{http://linkedin.com/in/pavel-panko-b43234114}{pavel-panko}} % Your phone number and email

\makeatletter
\def \printname {
  \begingroup
    \hfil{\namesize\bfseries \@name}\hfil
    \nameskip\break
  \endgroup
}
\makeatother


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Texas Tech University} \hfill {\bf Lubbock, TX}
\\ Doctor of Philosophy, Educational Psychology (Quantitative Methods)
\hfill May, 2020 \\ 
Master of Education, Educational Psychology (Quantitative Methods)
\hfill August, 2016
\\
\\{\bf Texas Tech University, Rawls College of Business} \hfill {\bf
  Lubbock, TX}
\\ Master of Science, Data Science \hfill May, 2020
\\
\\{\bf University of Kansas} \hfill {\bf Lawrence, KS}
\\Bachelor of Arts, Psychology (Minor in Social and Behavioral
Sciences Methodology) \hfill May, 2014

\end{rSection}

\begin{rSection}{Professional Qualifications}
  \begin{enumerate}
  \item[$\bullet$] Over seven years experience working in data
    analysis with a specialization in statistical
    programming. Passionate about open source statistical software, simulation experiments and
    high-performance computing.
  \item[$\bullet$] Applied research experience demonstrated by high-level published research articles \& reports in a
    variety of areas such as medicine, education, psychiatry, and statistics.
  \item[$\bullet$] Leadership experience garnered over five years of
    coordinating teams of researchers and scientists in academic,
    private, and government settings.
  \item[$\bullet$] Teaching experience in statistical methods as a
    technical trainer, consultant, and classroom instructor for
    both Graduate and Undergraduate students.
  \end{enumerate}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming \& Scripting & R, Python, BASH, git, C++, SQL, elisp \\
    Data Analysis \ & Mplus, SAS, LISREL \\
    Document Preparation \& Text Editing & \LaTeX, Markdown, Emacs,
                                           Microsoft Office \\
    Operating Systems & Arch Linux, Ubuntu, Fedora, Linux Mint \\ 
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

  \begin{rSubsection}{Institute for Measurement, Methodology, Analysis,
      \& Policy}{September 2014 - Present}{Senior Quantitative Analyst}{}
  \item Conducted advanced statistical analysis to test a variety of research hypotheses.
  \item Developed software in R to assist in data analysis for both clients and internal research teams.
  \item Guided clients in developing a data-driven narrative to answer
    extant research questions.
  \end{rSubsection}
  \begin{rSubsection}{Stats Camp}{June 2012 - Present}{Statistical
      Consultant}{}
  \item Instructed Stats Camp attendees in cutting-edge research methodology.
  \item Assisted attendees in applying newly-acquired methods to their research.
  \item Collaborated with Stats Camp instructors to publish novel research
    ideas.
  \end{rSubsection}
  \begin{rSubsection}{Center for Research Methods \& Data
      Analysis}{September 2012 - May, 2014}{Research Analyst}{}
  \item Analyzed large-scale national data sets using regression and structural equation modeling.
  \item Conducted simulation experiments in multilevel modeling.
  \item Coordinated statistical consulting sessions.
  \end{rSubsection}

\end{rSection}

\end{document}